---
title: "NYC Air Quality"
author: "Will Davis"
date: "2023-04-19"
output: html_document
---

```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
```

## Datta Source and cleaning

This data was provided by the City of New York(see link below for additional information), This data has been reduced to only contain information pertaining to FPM(fine particulate mater) with the goal of discovering where and when the most quantities can be found in NYC. 

Source: https://catalog.data.gov/dataset/air-quality
Source: http://nyc.gov/health/environmentdata 

```{r}
#importing cleaned data set of average measurements for the year
year_avg <- read.csv("C:\\Users\\willd\\OneDrive\\Desktop\\DataAnalysis\\AirQT\\Air_Quality_avg.csv")

#importing cleaned data set of seasonal information
season <- read.csv("C:\\Users\\willd\\OneDrive\\Desktop\\DataAnalysis\\AirQT\\Air_Quality.csv")

# on average is the FPM higher in the summer or the winter 
season_agg <- aggregate(season$Mean.mcg.per.cubic.meter, list(season$Season), FUN=mean)
colnames(season_agg) <- c("Season", "AVG_FPM")

# aggregate by part of city and year to find worst year and area 
city_agg <- aggregate(year_avg$Mean.mcg.per.cubic.meter, list(year_avg$Geo.Place.Name), FUN=mean)
colnames(city_agg) <- c("Area", "AVG_mcg_per_cubic_meter")
worst <- city_agg[order(city_agg$AVG_mcg_per_cubic_mete, decreasing = TRUE), ]
worst <- worst[1:10, ]
year_agg <- aggregate(year_avg$Mean.mcg.per.cubic.meter, list(year_avg$Year), FUN=mean)
colnames(year_agg) <- c("Year", "AVG_mcg_per_cubic_meter")

#Visuals 
# Bar chart of the trend over the years for the entire city
year_viz <- ggplot(year_agg, aes(x=Year, y=AVG_mcg_per_cubic_meter, group=1)) + 
  geom_line(color="red")+
  geom_point()+
  ggtitle("Average Fine Particulate Matter in NYC")
# visual of top 10 areas with the most FPM over
area_viz <- ggplot(worst, aes(x=Area, y=AVG_mcg_per_cubic_meter, fill=Area)) + 
  geom_bar(stat = "identity")+
  ggtitle("NYC Areas With Highest FPM")+
  theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 1))
# which season is worse visual 
season_viz <- ggplot(season_agg, aes(x= Season, y=AVG_FPM, fill=Season))+
  geom_col()+
  coord_flip()+
  scale_y_continuous(breaks = round(seq(min(0), max(15), by = 0.25)))+
  ggtitle("AVG FPM by Season")
```

## Findings 
Over 12 micro grams per cubic meter or "µg/m3" is considered harmful levels of FPM
FPM is most commonly caused by the burning of carbon based fuel such as fossil fuels or bio matter.  
The most FPM can be found in Midtown(CD5)
```{r areas}
plot(area_viz)
```

## Seasons
Though the concentration season to season is relatively similar there is a slightly greater concentration of FPM in the winter.
```{r season}
plot(season_viz)
```

## Over Time
Fortunately over the past few years the average concentration of FPM has been decreasing. 
```{r years}
plot(year_viz)
```
