---
title: "NYC Air Quality"
author: "Will Davis"
date: "2023-04-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Datta Source and cleaning

This data was provided by the City of New York(see link below for additional information), This data has been reduced to only contain information pertaining to FPM(fine particulate mater) with the goal of discovering where and when the most and least harmful quantities can be found in NYC. 

Source: https://catalog.data.gov/dataset/air-quality
Source: http://nyc.gov/health/environmentdata 

```{r cars}
summary(cars)
```

## Findings 

Over 12 micro grams per cubic meter or "µg/m3" is considered harmful levels of FPM
FPM is most commonly caused by the burning of carbon based fuel such as fossil fuels or bio matter.  
The most FPM can be found in ? during ? time of year, likely due to
The area with the least FPM is ? particularly during ? time of year.

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
